Appendix 1: sdmTMB statistical model description

### 2021-12-22 doc/appendix-model.Rmd
ADMB

Like AD Model Builder, TMB allows for parameters to be fit in phases and we include the `multiphase` argument in `sdmTMB::sdmTMBcontrol()` to allow this. 
For high-dimensional models (many of fixed and random effects), phased estimation may be faster and result in more stable convergence. 
In sdmTMB, phased estimation proceeds by first estimating all fixed-effect parameters contributing to the likelihood (holding random effects constant at initial values). 
In the second phase, the random-effect parameters (and their variances) are also estimated. 
Fixed-effect parameters are also estimated in the second phase and are initialized at their estimates from the first phase.

>>>>

Like AD Model Builder [@fournier2012ad], TMB allows for parameters to be fit in phases and we include the `multiphase` argument in `sdmTMB::sdmTMBcontrol()` to allow this. 
For high-dimensional models (many fixed and random effects), phased estimation may be faster and result in more stable convergence. 
In sdmTMB, phased estimation proceeds by first estimating all fixed-effect parameters contributing to the likelihood (holding random effects constant at initial values). 
In the second phase, the random-effect parameters (and their variances) are also estimated. 
Fixed-effect parameters are also estimated in the second phase and are initialized at their estimates from the first phase.
